---
title: "Stats 2 Project 1 Jerbs"
author: "Kito Patterson <br />  Andy Heroy <br /> Ryan Quincy Paul "
date: "2/7/2019"
output: html_document
---



### Load / View Data
[NYC Jobs](https://data.cityofnewyork.us/City-Government/NYC-Jobs/kpav-sd4t)
```{r}
df <- read.csv("datasets/NYC_Jobs.csv")

```

### Remove description columns and check datatypes
```{r echo=TRUE}
#jobs <- df[ -c(1,5,7,12,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28)]
#Staying positive and with names
jobs <- df[, names(df) %in% c("Agency","Posting.Type","X..Of.Positions","Civil.Service.Title","Level","Job.Category","Full.Time.Part.Time.indicator","Salary.Range.From","Salary.Frequency")]

#let's only keep annual salaries and fulltime
jobs <- jobs[jobs$Salary.Frequency == "Annual" & jobs$Full.Time.Part.Time.indicator == "F" & !is.na(jobs$Salary.Range.From),]
jobs <- jobs[jobs$Salary.Range.From > 0,]

#Code showing top salaries
library(dplyr)
jobs[jobs$Salary.Range.From > 0,] %>%
  arrange(desc(Salary.Range.From)) %>%
  select("Salary.Range.From") %>%
  slice(1:50)
```


### Exploratory Analysis
```{r EDAGraphs_and_such, fig.height=4}
mysummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)))
  names(result)<-c("N","Mean","SD","SE")
  return(result)
}



sumstats<-aggregate(Salary.Range.From~Level*Agency,data=jobs,mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])
#sumstats

pairs(jobs[, names(jobs) %in% c("Agency","Civil.Service.Title","Level","Job.Category","Salary.Range.From")])


library(ggplot2)
ggplot(sumstats,aes(x=Agency,y=Mean,group=Level,colour=Level))+
  ylab("Starting Salary")+
  geom_line()+
  geom_point()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SE,ymax=Mean+SE),width=.1)

#Same but without manager positions
jobs <- jobs[-grep("M", jobs$Level),]
sumstats<-aggregate(Salary.Range.From~Level*Agency,data=jobs,mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])
#sumstats

pairs(jobs[, names(jobs) %in% c("Agency","Civil.Service.Title","Level","Job.Category","Salary.Range.From")])

ggplot(sumstats,aes(x=Agency,y=Mean,group=Level,colour=Level))+
  ylab("Starting Salary")+
  geom_line()+
  geom_point()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SE,ymax=Mean+SE),width=.1)


#Code showing top salaries
library(dplyr)
jobs[jobs$Salary.Range.From > 0,] %>%
  arrange(desc(Salary.Range.From)) %>%
  select("Salary.Range.From") %>%
  slice(1:50)
  
#Same but without manager positions and removing salaries greater than 135000 (outliers)
jobs <- jobs[jobs$Salary.Range.From <135000,]

sumstats<-aggregate(Salary.Range.From~Level*Agency,data=jobs,mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])
#sumstats

pairs(jobs[, names(jobs) %in% c("Agency","Civil.Service.Title","Level","Job.Category","Salary.Range.From")])

ggplot(sumstats,aes(x=Agency,y=Mean,group=Level,colour=Level))+
  ylab("Starting Salary")+
  geom_line()+
  geom_point()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SE,ymax=Mean+SE),width=.1)

#Residual Plots 
```{r ResidualJazzed, fig.height=4}

#Initial Plots
model.fit<-aov(Salary.Range.From~Level+Agency+Level:Agency,data=jobs)
par(mfrow=c(1,2))
plot(model.fit$fitted.values,model.fit$residuals,ylab="Resdiduals",xlab="Fitted")
qqnorm(model.fit$residuals)

#Fancier plots
library(gridExtra)
myfits<-data.frame(fitted.values=model.fit$fitted.values,residuals=model.fit$residuals)

#Residual vs Fitted
plot1<-ggplot(myfits,aes(x=fitted.values,y=residuals))+ylab("Residuals")+
  xlab("Predicted")+geom_point()

#QQ plot of residuals  #Note the diagonal abline is only good for qqplots of normal data.
plot2<-ggplot(myfits,aes(sample=residuals))+
  stat_qq()+geom_abline(intercept=mean(myfits$residuals), slope = sd(myfits$residuals))

#Histogram of residuals
plot3<-ggplot(myfits, aes(x=residuals)) + 
  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
  geom_density(alpha=.1, fill="red")

grid.arrange(plot1, plot2,plot3, ncol=3)
```

``` {r Test Code}


# 
# par(mfrow=c(1,2))
# plot(review_difficulty,play_star_rating, xlab="Review Difficulty",ylab="Play Rating")
# new<-data.frame(review_difficulty=seq(30,300,.1))
# lines(seq(30,300,.1),predict(lm(play_star_rating~review_difficulty),newdata=new),col="red",lwd=4)
# 
# plot(as.factor(review_difficulty), play_star_rating,xlab="Review difficulty",ylab="Play Rating",title="Auto Data Set",col=c(7,32,57,82,107))


```
